### 2018-10-23 pilot_manuscript.Rmd
erin tests

In order to capture language's role in moral and political reasoning, @Graham2009 formulated the Moral Foundations Dictionary (MFD) in order to capture moral reasoning and justification as used in speech and text. The MFD is composed of 259 words, with around 50 words assigned to each of the five foundations. The researchers created a preliminary list of words that they believed would be associated with the five foundations. Then, using the Linguistic Inquiry and Word Count (LIWC; @Pennebaker2007) computer program, they analyzed transcripts of liberal and conservative Christian sermons in order to obtain frequencies of the occurrence of words from the researchers' initial list. The researchers manually checked the results from LIWC in order to make sure the results make sense given the contexts and rhetorical devices used in the sermons. Similar to previous research on Moral Foundations Theory, liberal ministers used *harm*, *fairness*, and *ingroup* words more often than conservative ministers. Conversely, conservative ministers used *authority* and *purity* words more often than liberal ministers. However, conservative ministers did not use *ingroup/loyalty* words more than liberals. Rather, liberal ministers used words pertaining to *ingroup/loyalty*, but in contexts that promote rebellion and independence - causes *opposite* to positive endorsements of that foundation [@Graham2009].

@@

Druckman, Jacobs, and Ostermeier (-@Druckman2004) also cited research from Iyengar and Kinder (1987) suggesting the news media affected perceptions of President Jimmy Carter's competence by emphasizing (read: priming) issues related to energy, defense, and the economy. This implies news media may affect perception of politicians based on where the media places emphasis. Other research into news media suggests certain media outlets, at least indirectly, may have an effect on the voting records of representatives in Congress [@Clinton2014]. Specifically, the researchers identified a pattern of declining support for President Bill Clinton's policies chiefly among Republicans in the House of Representatives after the Fox News Channel began broadcasting on cable and satellite systems in their districts. As Fox News was, at the time of its launch in 1996, the only outwardly ideological national news network, the reserachers were able to track its spread across the country and observe voting records of members of Congress both before and after Fox News' arrival [@Clinton2014]. The researchers concluded that members of Congress, excluding those newly elected at the time of Fox News Channel's emergence, attempted to anticipate resultant conservative-leaning shifts among their constituents by bolstering their conservative voting record before the next election [@Clinton2014].

@@

>>>>

In order to capture language's role in moral and political reasoning, @Graham2009 formulated the Moral Foundations Dictionary (MFD) in order to capture moral reasoning and justification as used in speech and text. The MFD is composed of 259 words, with around 50 words assigned to each of the five foundations. The researchers created a preliminary list of words that they believed would be associated with the five foundations. Then, using the Linguistic Inquiry and Word Count [LIWC; @Pennebaker2007] computer program, they analyzed transcripts of liberal and conservative Christian sermons in order to obtain frequencies of the occurrence of words from the researchers' initial list. The researchers manually checked the results from LIWC in order to make sure the results make sense given the contexts and rhetorical devices used in the sermons. Similar to previous research on Moral Foundations Theory, liberal ministers used *harm*, *fairness*, and *ingroup* words more often than conservative ministers. Conversely, conservative ministers used *authority* and *purity* words more often than liberal ministers. However, conservative ministers did not use *ingroup/loyalty* words more than liberals. Rather, liberal ministers used words pertaining to *ingroup/loyalty*, but in contexts that promote rebellion and independence - causes *opposite* to positive endorsements of that foundation [@Graham2009].

@@

@Druckman2004 also cited research from Iyengar and Kinder (1987) suggesting the news media affected perceptions of President Jimmy Carter's competence by emphasizing (read: priming) issues related to energy, defense, and the economy. This implies news media may affect perception of politicians based on where the media places emphasis. Other research into news media suggests certain media outlets, at least indirectly, may have an effect on the voting records of representatives in Congress [@Clinton2014]. Specifically, the researchers identified a pattern of declining support for President Bill Clinton's policies chiefly among Republicans in the House of Representatives after the Fox News Channel began broadcasting on cable and satellite systems in their districts. As Fox News was, at the time of its launch in 1996, the only outwardly ideological national news network, the reserachers were able to track its spread across the country and observe voting records of members of Congress both before and after Fox News' arrival [@Clinton2014]. The researchers concluded that members of Congress, excluding those newly elected at the time of Fox News Channel's emergence, attempted to anticipate resultant conservative-leaning shifts among their constituents by bolstering their conservative voting record before the next election [@Clinton2014].

@@

```{r update-mlm, include = FALSE}

#harm_final_data clean up
harm_final_data$percent = harm_final_data$Freq / harm_final_data$wordcount *100
harm_final_data$lean = factor(harm_final_data$Source, 
                              levels = names(table(harm_final_data$Source)),
                              labels = c("Conservative1", "Conservative",
                                  "Liberal1", "Liberal"))
harm_final_data$lean = gsub("1", "", harm_final_data$lean)

harm_final_data$weighted = harm_final_data$percent*harm_final_data$valence

#boring models first

#final model
modelfinal = lme(percent ~ valence*lean,
                 data = harm_final_data,
                 method = "ML", 
                 na.action = "na.omit", 
                 random = list(~1|Var1, ~1|Source))
summary(modelfinal)

with(harm_final_data, tapply(percent, list(lean), mean))
with(harm_final_data, tapply(valence, list(lean), mean, na.rm = T))
with(harm_final_data, tapply(weighted, list(lean), mean, na.rm = T))

modelfinal = lme(weighted ~ lean,
                 data = harm_final_data,
                 method = "ML", 
                 na.action = "na.omit", 
                 random = list(~1|Var1, ~1|Source))
summary(modelfinal)
